Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
cover page and margins
correct typo in dependency-sets section

\title{Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms}

\author{}

\date{}

@@

\maketitle

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

>>>>

%\title{Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms}

%\author{}

%\date{}

@@

%\maketitle

\input{cover}

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}
